Modelling the emergence of whisker barrels

### 2020-07-02 paper/briefpaper/brief.tex
More caption tweaking

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png}
  \captionof{figure}{
    \MPthreePred{
      Two simulated whisker barrel manipulations.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. The model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by a
      reduction of the competition parameter, $\epsilon$, in the expression
      $\chi_i$ (Eq.\,\ref{eq:comp}) for the C3 thalamocortical projection. For
      C3, $\epsilon$ is replaced by $m\,\epsilon$, where $m$ is a scalar
      multiplier. For the rest of the projections, $\chi_i$ is left unchanged
      and all other parameters are identical to those reported in
      Fig.\,\ref{fig:main}C. The pattern formed after 30000 steps with
      $m=0.64$. Barrel C3 is reduced in size as its axon branching competes
      less strongly with its neighbours, whose area is slightly
      increased. \textbf{D} Individual barrel area plotted vs.~$m$ shows that
      as $m$ is reduced, the area of C3 (blue squares) goes down, disappearing
      for $m\approx0.5$, whereas the average area of neighbouring barrels
      (triangles) increases. Scale bars are 1\,mm.
    }
  }
  \label{fig:fgf8}
\end{center}

>>>>

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png} \captionof{figure}{
    \MPthreePred{Two simulated whisker barrel manipulations.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. The model parameters match those in
      Fig.\,\ref{fig:main}C.  Scale bars are 1\,mm. \textbf{C} Simulating
      whisker trimming by a reduction of the competition parameter,
      $\epsilon$, in the expression $\chi_i$ (Eq.\,\ref{eq:comp}) for the C3
      thalamocortical projection. For C3, $\epsilon$ is replaced by
      $m\,\epsilon$, where $m$ is a scalar multiplier. For the rest of the
      projections, $\chi_i$ is left unchanged and all other parameters are
      identical to those reported in Fig.\,\ref{fig:main}C. The pattern formed
      after 30000 steps with $m=0.64$. Barrel C3 is reduced in size as its
      axon branching competes weakly with its neighbours, whose area is
      slightly increased. \textbf{D} Individual barrel area (mm$^2$) plotted
      vs.~$m$ for C3 (black squares) shows that as $m$ is reduced, its area
      goes down, disappearing for $m\approx0.5$, whereas the mean area of
      neighbouring barrels B3, C2, C4, D2 \& D3 (grey circles) increases. The
      dotted grey line indicates $m=0.64$ for comparison with panel C.}}
  \label{fig:fgf8}
\end{center}
